An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet  =

### 2021-06-07 CMPSpaper_writing/CMPSpaper_writing.Rmd
edited the result and conclusion section

For the third result of Hamby 44, we changed a parameter used in the data-processing procedure. `span1=0.25` is used in previous results, and we changed it to `span1=0.75` \wj{in this case to make bullet signatures capture more global patterns XXX}.
<!-- For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the  = ; however, in this example we used `span1=0.75` and changed the characteristic of those  = . -->
As we can see in \autoref{fig:result3_44}, changing some characteristics of bullet signatures will also change the final CMPS results. 
\autoref{tab:table1} presents some summary statistics of the Hamby 44 results above. These summary statistics are used to show the separation between the KM and KNM groups in the distribution of both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.

\wj{XXX talk about the table: Not exhaustive, more research is needed to cross-validate the parameters}
<!-- this is figure 5 -->

@@

We presented the CMPS package, an open-source implementation of the congruent matching profile segments (CMPS) algorithm. The CMPS algorithm was proposed by NIST in 2019 and was made for objective tool marks comparisons. In this paper, functions included in the package were illustrated along with the basic logic of the CMPS algorithm. 
And we used a small dataset included in the package as an example to explain the usage of the package. Some graphing tools were also implemented in the package so that users can visualize results and have a better understanding of both the algorithm and the results. We also applied the algorithm to two datasets in Hamby study (Hamby set 252 and Hamby set 44), and the results we obtained were promising.

From the results of both Hamby set 252 and 44, we can see that the CMPS scores of KM comparisons computed by `extract_feature_cmps` were able to be separated from those of KNM comparisons. And at the same time, we can see that CMPS algorithm is sensitive to the choice of parameters such as segment length, number of peaks detected at each segment scale, and congruency tolerance. Some parameter choices are better in the sense that they can enlarge the separation between the KM comparisons and the KNM comparisons. And the best set of parameters depend on the dataset being used, and the choice of parameters has not been, but should be, cross-validated.

Our open-source implementation introduces the CMPS algorithm to R community and allows everyone to use it for their own projects. It would also facilitate future studies on parameter cross-validation and the development of statistical methods to modeling KM and KNM CMPS score distributions.

>>>>

For the third result of Hamby 44, we changed a parameter used in the data-processing procedure. `span1=0.25` is used in previous results, and we changed it to `span1=0.75` \wj{in this case to make bullet signatures capture more global patterns XXX}.
<!-- For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the  = ; however, in this example we used `span1=0.75` and changed the characteristic of those  = . -->
As we can see in \autoref{fig:result3_44}, changing some characteristics of bullet signatures will also change the final CMPS results. 
\autoref{tab:table1} presents some summary statistics of the Hamby 44 results above. These summary statistics are used to show the separation between the KM and KNM groups in the distribution of both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$. As shown in \autoref{tab:table1}, some parameter settings are better than others in terms of the separation between the two distributions. \wj{However, we are not suggesting any set of parameters to users since further research is needed to provide a comprehensive cross-validation on these parameters, which can be facilitated by an open-source implementation of the CMPS algorithm.}

<!-- this is figure 5 -->

@@

In this paper we presented the CMPS package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and applied it to two datasets in Hamby study [@hamby] to show its potential for further research. 
The CMPS algorithm was proposed by NIST in 2019 and was made for objective tool marks comparisons. 
We introduced the basic logic of the CMPS algorithm and how it is implemented in the CMPS package. We also showcased the functionality of the CMPS package with a small dataset example that is included in the package.
In the CMPS package we also implemented some graphing tools for users to visualize results generated by our functions and to have a better understanding of both the algorithm and the results.

Additionally, we applied the CMPS package to two datasets in Hamby study (Hamby set 252 and Hamby set 44), and the results we obtained were promising since we were able to reproduce the results in @cmps qualitatively and achieve a clear separation between the known-match (KM) comparisons and known-nonmatch (KNM) comparisons. However, the results of Hamby set 44 suggested that the CMPS method is sensitive to the choice of parameters in the algorithm, such as the length of basis segments and the number of peaks detected at each segment scale. This indicates that further research is needed to provide a comprehensive cross-validation on parameters used the algorithm. Moreover, we might want to compare the two versions of the CMPS algorithm in the future as well.

The CMPS package as an open-source implementation introduces the CMPS algorithm to the `R` community and allows people to use it for their own projects. It would also facilitate future studies on parameter cross-validations, method comparisons, and the development of statistical methods for modeling KM and KNM CMPS score distributions, which can potentially be used to estimate error rates or define an identification criterion.
